Proposed Solution

### 2016-02-27 ICFP/formalism.tex
start formlism of probablistic

A primary concern in any machine learning type task is to minimize both false negatives and false positives.
In the context of configuration file verification,
  a false positive is when \app reports an error on a valid confiuration file and
  a false negative is when \app fails to reports an error on an invalid confiuration file.
Too many false positives will cause users to ignore the reported error\cite{}.
However, since the cost of system failure is so high from a misconfiguration, \app propritzes the minimization of false negatives.

While a traditional classififcation learning machine learning approach can reduce both of these situations, generally, there is can be no garuntee that all false negatives will be eliminated.
Instead of building classification models over the learning set (such as an SVM), we learn the largest set of rules that all correct configuration files satisfy.
In this way, \app can garuntee that, over the set of rules we consider, there will be no false negatives that could have been caught with the given learning set.
The only case of a false negative can be when there was no evidece of such a rule in the learning set - we cannot generate rules from nothing.

$\mathcal{L}$ = Learned Rules\\
$\mathcal{C}$ = Correct Configuration File Learning Set\\
$\mathcal{R}$ = Reported Rules\\
$\mathcal{T}$ = True Rules\\

@@

The learned rule set, $\mathcal{L}$, is represented as a type, where the type must support a particular interface (called a typeclass in Haskell) to be compatible with our system.
The three methods of this typeclass and the associated specification will help to show completeness of our system.
The functions of this typeclass will be used, invisibly to the user, to make the overall system run.
As long as the specifications for each function are met, \app can garuntee completness.

@@

\subsection{learn}
  For a single given file in the intermediate representation format, learn the full set of rules on that file.
  By overfitting to each file, we can eventually garuntee the completness of \app.
  The specification of this function is the obvious reduction of the Considered Set definition.

@@

\subsection{merge}
  Merging the sets of rules from two files to build a new set that is true over both files is the most difficult and important function a rule must implement.
  This is generally implemented as a filter over the union of the two set, but may vary slightly.
  The second predicate of formal specification states that the rule cannot conflict with other existing rules.
  \begin{align*}
  \text{merge }& Set1 \: Set2= \{r \mid \\
    & r \in \text{Set1} \cup \text{Set2}\ \land \\
    & \exists file\ \forall r' \in \text{Set1} \cup \text{Set2}, r(file) \land r'(file) \} \\
  \end{align*}

\subsection{check}
  To check a file by using a rule set, we simply take all the rules that are releveant to the user's file.
  Rules that are relavent are the ones where both parts of the ordering are present.
  We learn the rule set for the user file, and every rule in the learned set must be present in the user file.

>>>>

A primary concern in any machine learning type task is to minimize both false negatives and false positives.
In the context of configuration file verification,
  a false positive is when \app reports an error on a valid configuration file and
  a false negative is when \app fails to reports an error on an invalid configuration file.
Too many false positives will cause users to ignore the reported error\cite{}.
However, since the cost of system failure is so high from a misconfiguration, \app prioritizes the minimization of false negatives.

While a traditional classification learning machine learning approach can reduce both of these situations, generally, there is can be no guarantee that all false negatives will be eliminated.
Instead of building classification models over the learning set (such as an SVM), we learn the largest set of rules that all correct configuration files satisfy.
In this way, \app can guarantee that, over the set of rules we consider, there will be no false negatives that could have been caught with the given learning set.
The only case of a false negative can be when there was no evidence of such a rule in the learning set - we cannot generate rules from nothing.

$\mathcal{C}$ = Correct Configuration File Learning Set\\
$\mathcal{L}$ = Learned Rules\\
$\mathcal{R}$ = Reported Rules\\
$\mathcal{T}$ = True Rules\\

@@

\section{Incorrect Learning Set}
We have a database of incorrect configuration files.
Rather than manually correct each file, we observe that the files are usually incorrect in only one or two lines.
We then extend the previous formalism to handle probabilistic learning, when we have a collection of such files.

$\mathcal{CP}$ = Incorrect Configuration File Learning Set\\
$\mathcal{LP}$ = Probabilistically Learned Rules\\
$\mathcal{RP}$ = Probabilistically Reported Rules\\

\begin{flalign*}
\mathcal{LP}& =\ \{ r\ \mid \\
  & \Pi file \in \mathcal{CP},\ r(file)\  \land\\
  & \exists file \in \mathcal{CP},\ r(file) \text{ is non-trivial} \} \\
\mathcal{RP}& =\ \{ r\ \mid \\
  & r \in \mathcal{LP}\ \land\\
  & \neg r(userfile) \}&\\
\end{flalign*}

Where $\Pi$ indicates some percentage of the files in CP.
In this case, we can no longer conclude that \app is complete.

\begin{flalign}
& \forall r \in \mathcal{T}, r \in \mathcal{RP} \qquad \text{[Incomplete]} \\
& \exists r \in \mathcal{RP}, r \notin \mathcal{T} \qquad \text{[Unsound]}
\end{flalign}

\section{Implementation}

The learned rule set, $\mathcal{L}$, is represented as a type, where the type must support a particular interface (called a typeclass in Haskell) to be compatible with our system.
The three methods of this typeclass and the associated specification will help to show completeness of our system.
The functions of this typeclass will be used, invisibly to the user, to make the overall system run.
As long as the specifications for each function are met, \app can guarantee completeness.

@@

\subsection{learn}
  For a single given file in the intermediate representation format, learn the full set of rules on that file.
  By overfitting to each file, we can eventually guarantee the completeness of \app.
  The specification of this function is the obvious reduction of the Considered Set definition.

@@

\subsection{merge}
  Merging the sets of rules from two files to build a new set that is true over both files is the most difficult and important function a rule must implement.
  This is generally implemented as a filter over the union of the two set, but may vary slightly.
  The second predicate of formal specification states that the rule cannot conflict with other existing rules.
  \begin{align*}
  \text{merge* }& Set1 \: Set2= \{r \mid \\
    & r \in \text{Set1} \cup \text{Set2}\ \land \\
    & \exists file\ \forall r' \in \text{Set1} \cup \text{Set2}, r(file) \land r'(file) \} \\
  \end{align*}

\subsection{check}
  To check a file by using a rule set, we simply take all the rules that are relevant to the user's file.
  Rules that are relevant are the ones where both parts of the ordering are present.
  We learn the rule set for the user file, and every rule in the learned set must be present in the user file.
